Implementing \Kwd{DNS} in \Kwd{C0}

### 2017-12-13 paper.tex
add link to github (feel free to move)

\begin{abstract}
  We have implemented a \Kwd{DNS} server in the \Kwd{C0} language, and
  evaluated it for both safety and performance.
\end{abstract}

>>>>

\begin{abstract}
  We have implemented a \Kwd{DNS} server in the \Kwd{C0} language
  called \Kwd{c0ns},\footnote{Source code available on GitHub:
    \url{http://www.github.com/jonsterling/c0ns.git}.} and evaluated it for
  both safety and performance.
\end{abstract}
